% chktex-file 8
% chktex-file 13

\documentclass{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage[margin=0.75in]{geometry}

\graphicspath{ {./images/} }

\definecolor{darkblue}{rgb}{0, 0, 20}

\hypersetup{
    colorlinks=true,
    urlcolor=darkblue,
    linkcolor=blue,
    filecolor=magenta,
    citecolor=blue,
}

\title{EgoCVR: An Egocentric Benchmark for Fine-Grained Composed Video Retrieval}
\author{Thomas Hummel, Shyamgopal Karthik, Mariana-Iuliana Georgescu, Zeynep Akata}
\date{}
\setlength{\parindent}{0pt}

\begin{document}

\maketitle

\begin{center}\textbf{Accepted for ECCV 2024 (\href{https://arxiv.org/pdf/2407.16658}{Paper}) (\href{https://github.com/ExplainableML/EgoCVR}{GitHub})}\end{center}

The authors resolve issues with the WebVid-CoVR-Test dataset, specifically most of the modification texts involve a color, shape, or object change which doesn't require temporal understanding, and that captions are only considered similar if they have a one word difference. Also, they introduce a training-free method that achieves stronger performance on their new evaluation dataset.

\section*{Motivation}

85\% of samples in the WebVid-CoVR-Test dataset focused on object-centered modifications, such as a color, shape, or object change, which doesn't require temporal understanding and only requires image-level understanding. Also, the WebVid-CoVR-Test dataset was created by searching for single-word differences in video captions, which does not properly evaluate the generalizability to different prompt formats.

\section*{Method}

\subsection*{Evaluation Dataset}
\begin{enumerate}
    \item 1,250 long videos are taken from the Ego4D FHO dataset.
    \item 155k annotated clips are extracted from the videos, ranging from 2 to 8 seconds.
    \item The clips are filtered for temporal overlap, resulting in 9k distinct clips.
    \item Pairs are manually identified from video clips in the same video, looking for similarity in captions, except for a single action or object change.
    \item 
\end{enumerate}

\section*{Limitations}

\end{document}